R tools for accessing research literature for text mining

### 2019-08-23 manuscript.Rmd
acknowledgements maelle
fix #14 add what type of fulltext avail for publishers in table 1

Data Provider                      | Content Type            | rOpenSci Package         | Documentation
---------------------------------- | ---------------------   | ------------------------ | -------------
Crossref                           | Metadata                | rcrossref/crminer        | [^1]
DataCite                           | Metadata                | rdatacite                | [^2]
Biodiversity Heritage Library      | Full text/Metadata      | rbhl                     | [^3]
Public Library of Science (PLoS)   | Full text/altmetrics    | rplos                    | [^4]
Scopus (Elsevier)                  | Full text/Metadata      | fulltext                 | [^5]
arXiv                              | Full text/Metadata      | aRxiv                    | [^6]
Biomed Central (via Springer)      | Full text/Metadata      | fulltext                 | [^7]
bioRxiv                            | Full text/Metadata      | fulltext                 | [^8]
PMC/Pubmed (via Entrez)            | Full text/Metadata      | rentrez                  | [^9]
Europe PMC                         | Full text/Metadata      | europepmc                | [^10]
Microsoft Academic Search          | Metadata                | microdemic               | [^11]
Directory of Open Access Journals  | Metadata                | jaod                     | [^12]
JSTOR Data for Research            | Full text               | jstor                    | [^13]
ORCID                              | Metadata                | rorcid                   | [^14]
Wikimedia's Citoid                 | Citations               | rcitoid                  | [^15]
Open Citation Corpus               | Citations               | citecorp                 | [^16]
Fatcat                             | Metadata                | none                     | [^17]
SHERPA/RoMEO                       | Journal Level Metadata  | rromeo                   | [^18]
CORE                               | Full text/Metadata      | rcoreoa                  | [^19]
Dissemin                           | Metadata                | dissemr                  | [^20]

>>>>

Data Provider                      | Content Type                 | rOpenSci Package   | Documentation
---------------------------------- | ---------------------------- | ------------------ | -------------
Crossref                           | Metadata                     | rcrossref/crminer  | [^1]
DataCite                           | Metadata                     | rdatacite          | [^2]
Biodiversity Heritage Library      | Full text/Metadata           | rbhl               | [^3]
Public Library of Science (PLoS)   | Full text (pdf/xml)/Metadata | rplos              | [^4]
Scopus (Elsevier)                  | Full text (pdf/xml)/Metadata | fulltext           | [^5]
arXiv                              | Full text (pdf)/Metadata     | aRxiv              | [^6]
Biomed Central (via Springer)      | Full text (pdf)/Metadata     | fulltext           | [^7]
bioRxiv                            | Full text (pdf)/Metadata     | fulltext           | [^8]
PMC/Pubmed (via Entrez)            | Full text (pdf/xml)/Metadata | rentrez            | [^9]
Europe PMC                         | Full text (pdf/xml)/Metadata | europepmc          | [^10]
Microsoft Academic Search          | Metadata                     | microdemic         | [^11]
Directory of Open Access Journals  | Metadata                     | jaod               | [^12]
JSTOR Data for Research            | Full text                    | jstor              | [^13]
ORCID                              | Metadata                     | rorcid             | [^14]
Wikimedia's Citoid                 | Citations                    | rcitoid            | [^15]
Open Citation Corpus               | Citations                    | citecorp           | [^16]
Fatcat                             | Metadata                     | none               | [^17]
SHERPA/RoMEO                       | Journal Level Metadata       | rromeo             | [^18]
CORE                               | Full text (pdf)/Metadata     | rcoreoa            | [^19]
Dissemin                           | Metadata                     | dissemr            | [^20]

### 2019-08-23 manuscript.tex
fix #14 add what type of fulltext avail for publishers in table 1

\begin{longtable}[]{@{}llll@{}}
\toprule
Data Provider & Content Type & rOpenSci Package &
Documentation\tabularnewline
\midrule
\endhead
Crossref & Metadata & rcrossref/crminer & \footnote{\url{https://api.crossref.org}}\tabularnewline
DataCite & Metadata & rdatacite & \footnote{\url{https://support.datacite.org/docs/api}}\tabularnewline
Biodiversity Heritage Library & Full text/Metadata & rbhl & \footnote{\url{http://bit.ly/KYQ1Rd}}\tabularnewline
Public Library of Science (PLoS) & Full text/altmetrics & rplos &
\footnote{\url{http://api.plos.org/solr}}\tabularnewline
Scopus (Elsevier) & Full text/Metadata & fulltext & \footnote{\url{http://bit.ly/J9S616}}\tabularnewline
arXiv & Full text/Metadata & aRxiv & \footnote{\url{https://arxiv.org/help/api/index}}\tabularnewline
Biomed Central (via Springer) & Full text/Metadata & fulltext &
\footnote{\url{https://dev.springer.com/}}\tabularnewline
bioRxiv & Full text/Metadata & fulltext & \footnote{\url{http://www.biorxiv.org/}}\tabularnewline
PMC/Pubmed (via Entrez) & Full text/Metadata & rentrez & \footnote{\url{https://www.ncbi.nlm.nih.gov/books/NBK25500}}\tabularnewline
Europe PMC & Full text/Metadata & europepmc & \footnote{\url{https://azure.microsoft.com/en-us/services/cognitive-services}}\tabularnewline
Microsoft Academic Search & Metadata & microdemic & \footnote{\url{https://dev.labs.cognitive.microsoft.com/docs/services/56332331778daf02acc0a50b/operations/565d9001ca73072048922d97}}\tabularnewline
Directory of Open Access Journals & Metadata & jaod & \footnote{\url{https://doaj.org/api/v1/docs}}\tabularnewline
JSTOR Data for Research & Full text & jstor & \footnote{\url{https://www.jstor.org/dfr/}}\tabularnewline
ORCID & Metadata & rorcid & \footnote{\url{https://pub.orcid.org/}}\tabularnewline
Wikimedia's Citoid & Citations & rcitoid & \footnote{\url{https://en.wikipedia.org/api/rest_v1/\#/Citation/getCitation}}\tabularnewline
Open Citation Corpus & Citations & citecorp & \footnote{\url{http://opencitations.net/}}\tabularnewline
Fatcat & Metadata & none & \footnote{\url{https://fatcat.wiki/}}\tabularnewline
SHERPA/RoMEO & Journal Level Metadata & rromeo & \footnote{\url{http://www.sherpa.ac.uk/romeo/apimanual.php?la=en\&fIDnum=\%7C\&mode=simple}}\tabularnewline
CORE & Full text/Metadata & rcoreoa & \footnote{\url{https://core.ac.uk/}}\tabularnewline
Dissemin & Metadata & dissemr & \footnote{\url{https://dissemin.readthedocs.io/en/latest/api.html}}\tabularnewline
\bottomrule
\end{longtable}

@@

Elsevier is one of the largest publishers. Most of their articles are
not open access. However, they have a numbrer of advantages if you have
access to their articles: they are one of the few publishers to provide
machine readable XML (many publishers do have XML versions of articles,
but do not provide it); they are one of the few (two) publishers part of
Crossref's text and data mining program. The packages
\href{https://github.com/ropensci/fulltext}{fulltext} and
\href{https://github.com/ropensci/crminer}{crminer} can be used to
access Elsevier articles through Crossref's TDM program. There's an
interface to Scopus article search within
\href{https://github.com/ropensci/fulltext}{fulltext}.

@@

arXiv and bioRxiv are preprint publishers, the former in existence for
many years, and the latter new on the scene. You can access articles
from these publishers through
\href{https://github.com/ropensci/fulltext}{fulltext}. arXiv does
provide a web API that we hook into; bioRxiv does not, but we can get
you articles nonetheless.

@@

Fatcat is a project from Ben Newbold of the Internet Archive Labs. It is
a ``versioned, publicly-editable catalog of research publications:
journal articles, conference proceedings, pre-prints, blog posts''.
Fatcat is currently does not have an R client, but is used inside of the
\href{https://github.com/ropensci/fulltext}{fulltext} package.

@@

All scripts and data used in this paper can be found in the permanent
data archive Zenodo under the digital object identifier (DOI). This DOI
corresponds to a snapshot of the GitHub repository at
\url{https://github.com/ropensci/textmine}. Software can be found at
\url{https://github.com/ropensci/xxx}, xxxx, all under MIT licenses.

>>>>

\begin{longtable}[]{@{}llll@{}}
\toprule
Data Provider & Content Type & rOpenSci Package &
Documentation\tabularnewline
\midrule
\endhead
Crossref & Metadata & rcrossref/crminer & \footnote{\url{https://api.crossref.org}}\tabularnewline
DataCite & Metadata & rdatacite & \footnote{\url{https://support.datacite.org/docs/api}}\tabularnewline
Biodiversity Heritage Library & Full text/Metadata & rbhl & \footnote{\url{http://bit.ly/KYQ1Rd}}\tabularnewline
Public Library of Science (PLoS) & Full text (pdf/xml)/Metadata & rplos
& \footnote{\url{http://api.plos.org/solr}}\tabularnewline
Scopus (Elsevier) & Full text (pdf/xml)/Metadata & fulltext & \footnote{\url{http://bit.ly/J9S616}}\tabularnewline
arXiv & Full text (pdf)/Metadata & aRxiv & \footnote{\url{https://arxiv.org/help/api/index}}\tabularnewline
Biomed Central (via Springer) & Full text (pdf)/Metadata & fulltext &
\footnote{\url{https://dev.springer.com/}}\tabularnewline
bioRxiv & Full text (pdf)/Metadata & fulltext & \footnote{\url{http://www.biorxiv.org/}}\tabularnewline
PMC/Pubmed (via Entrez) & Full text (pdf/xml)/Metadata & rentrez &
\footnote{\url{https://www.ncbi.nlm.nih.gov/books/NBK25500}}\tabularnewline
Europe PMC & Full text (pdf/xml)/Metadata & europepmc & \footnote{\url{https://azure.microsoft.com/en-us/services/cognitive-services}}\tabularnewline
Microsoft Academic Search & Metadata & microdemic & \footnote{\url{https://dev.labs.cognitive.microsoft.com/docs/services/56332331778daf02acc0a50b/operations/565d9001ca73072048922d97}}\tabularnewline
Directory of Open Access Journals & Metadata & jaod & \footnote{\url{https://doaj.org/api/v1/docs}}\tabularnewline
JSTOR Data for Research & Full text & jstor & \footnote{\url{https://www.jstor.org/dfr/}}\tabularnewline
ORCID & Metadata & rorcid & \footnote{\url{https://pub.orcid.org/}}\tabularnewline
Wikimedia's Citoid & Citations & rcitoid & \footnote{\url{https://en.wikipedia.org/api/rest_v1/\#/Citation/getCitation}}\tabularnewline
Open Citation Corpus & Citations & citecorp & \footnote{\url{http://opencitations.net/}}\tabularnewline
Fatcat & Metadata & none & \footnote{\url{https://fatcat.wiki/}}\tabularnewline
SHERPA/RoMEO & Journal Level Metadata & rromeo & \footnote{\url{http://www.sherpa.ac.uk/romeo/apimanual.php?la=en\&fIDnum=\%7C\&mode=simple}}\tabularnewline
CORE & Full text (pdf)/Metadata & rcoreoa & \footnote{\url{https://core.ac.uk/}}\tabularnewline
Dissemin & Metadata & dissemr & \footnote{\url{https://dissemin.readthedocs.io/en/latest/api.html}}\tabularnewline
\bottomrule
\end{longtable}

@@

Elsevier is one of the largest publishers. Scopus is one of their
products, a searchable database of articles. Most of their articles are
not open access. However, they have a number of advantages if you have
access to their articles: they are one of the few publishers to provide
machine readable XML (many publishers do have XML versions of articles,
but do not provide it, as mentioned in the Introduction); they are one
of the few (two) publishers that take part in Crossref's text and data
mining program. The packages
\href{https://github.com/ropensci/fulltext}{fulltext} and
\href{https://github.com/ropensci/crminer}{crminer} can be used to
access Elsevier articles through Crossref's TDM program. There's an
interface to Scopus article search within
\href{https://github.com/ropensci/fulltext}{fulltext}.

@@

arXiv and bioRxiv are preprint publishers, the former in existence for
many years, and the latter new on the scene. Preprints are scholarly
articles that are generally not peer-reviewed, but that for the most
part will later be published in a different peer-review publication. You
can access articles from these publishers through
\href{https://github.com/ropensci/fulltext}{fulltext}. arXiv does
provide a web API that we hook into; bioRxiv does not, but we can get
you articles nonetheless.

@@

Fatcat is a project from Ben Newbold of the Internet Archive Labs. It is
a ``versioned, publicly-editable catalog of research publications:
journal articles, conference proceedings, preprints, blog posts''.
Fatcat is currently does not have an R client, but is used inside of the
\href{https://github.com/ropensci/fulltext}{fulltext} package.

@@

All scripts and data used in this paper can be found in the permanent
data archive Zenodo under the digital object identifier (DOI). This DOI
corresponds to a snapshot of the GitHub repository at
\url{https://github.com/ropensci/textmine}. Software can be found at
\url{https://github.com/ropensci}, all under MIT licenses.
